\documentclass[11pt, a4paper, oneside]{article}
\usepackage[margin=1in]{geometry}    
\geometry{letterpaper}       
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Deactivate to begin paragraphs with an indent rather than an empty line
\usepackage{amsfonts, amscd, amssymb, amsthm, amsmath}
\usepackage{pdfsync}  %leaves makers for tex searching
\usepackage{enumerate}
\usepackage{multicol}
\usepackage[pdftex,bookmarks]{hyperref}
\usepackage{enumitem}
\usepackage{amsthm}
\usepackage{kbordermatrix}

\theoremstyle{plain}
	\newtheorem*{thm*}{Theorem}
	
\theoremstyle{plain}
	\newtheorem*{prop*}{Proposition}
	
\theoremstyle{plain}
	\newtheorem*{lemma*}{Lemma}


\renewcommand{\baselinestretch}{1.25}



\setlength\parindent{0pt}

%%% Theorems %%%--------------------------------------------------------- 
\theoremstyle{plain}
	\newtheorem{thm}{Theorem}[section]
	\newtheorem{lemma}[thm]{Lemma}
	\newtheorem{prop}[thm]{Proposition}
	\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
	\newtheorem*{defn}{Definition}
	\newtheorem{remark}{Remark}
\theoremstyle{example}
	\newtheorem*{example}{Example}


%%% Environments %%%--------------------------------------------------------- 
\newenvironment{ans}{\color{black}\medskip \paragraph*{\emph{Answer}.}}{\hfill \break  $~\!\!$ \dotfill \medskip }
\newenvironment{sketch}{\medskip \paragraph*{\emph{Proof sketch}.}}{ \medskip }
\newenvironment{summary}{\medskip \paragraph*{\emph{Summary}.}}{  \hfill \break  \rule{1.5cm}{0.4pt} \medskip }
\newcommand\Ans[1]{\color{black}\hfill \emph{Answer:} {#1}}


%%% Pictures %%%--------------------------------------------------------- 
%%% If you need to draw pictures, tikzpicture is one good option. Here are some basic things I always use:
\usepackage{tikz}
\usetikzlibrary{arrows}
\tikzstyle{V}=[draw, fill =black, circle, inner sep=0pt, minimum size=2pt]
\newcommand\TikZ[1]{\begin{matrix}\begin{tikzpicture}#1\end{tikzpicture}\end{matrix}}



%%% Color  %%%---------------------------------------------------------
\usepackage{color}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\NOTE}[1]{{\color{blue}#1}}
\newcommand{\MOVED}[1]{{\color{gray}#1}}


%%% Alphabets %%%---------------------------------------------------------
%%% Some shortcuts for my commonly used special alphabets and characters.
\def\cA{\mathcal{A}}\def\cB{\mathcal{B}}\def\cC{\mathcal{C}}\def\cD{\mathcal{D}}\def\cE{\mathcal{E}}\def\cF{\mathcal{F}}\def\cG{\mathcal{G}}\def\cH{\mathcal{H}}\def\cI{\mathcal{I}}\def\cJ{\mathcal{J}}\def\cK{\mathcal{K}}\def\cL{\mathcal{L}}\def\cM{\mathcal{M}}\def\cN{\mathcal{N}}\def\cO{\mathcal{O}}\def\cP{\mathcal{P}}\def\cQ{\mathcal{Q}}\def\cR{\mathcal{R}}\def\cS{\mathcal{S}}\def\cT{\mathcal{T}}\def\cU{\mathcal{U}}\def\cV{\mathcal{V}}\def\cW{\mathcal{W}}\def\cX{\mathcal{X}}\def\cY{\mathcal{Y}}\def\cZ{\mathcal{Z}}

\def\AA{\mathbb{A}} \def\BB{\mathbb{B}} \def\CC{\mathbb{C}} \def\DD{\mathbb{D}} \def\EE{\mathbb{E}} \def\FF{\mathbb{F}} \def\GG{\mathbb{G}} \def\HH{\mathbb{H}} \def\II{\mathbb{I}} \def\JJ{\mathbb{J}} \def\KK{\mathbb{K}} \def\LL{\mathbb{L}} \def\MM{\mathbb{M}} \def\NN{\mathbb{N}} \def\OO{\mathbb{O}} \def\PP{\mathbb{P}} \def\QQ{\mathbb{Q}} \def\RR{\mathbb{R}} \def\SS{\mathbb{S}} \def\TT{\mathbb{T}} \def\UU{\mathbb{U}} \def\VV{\mathbb{V}} \def\WW{\mathbb{W}} \def\XX{\mathbb{X}} \def\YY{\mathbb{Y}} \def\ZZ{\mathbb{Z}}  

\def\fa{\mathfrak{a}} \def\fb{\mathfrak{b}} \def\fc{\mathfrak{c}} \def\fd{\mathfrak{d}} \def\fe{\mathfrak{e}} \def\ff{\mathfrak{f}} \def\fg{\mathfrak{g}} \def\fh{\mathfrak{h}} \def\fj{\mathfrak{j}} \def\fk{\mathfrak{k}} \def\fl{\mathfrak{l}} \def\fm{\mathfrak{m}} \def\fn{\mathfrak{n}} \def\fo{\mathfrak{o}} \def\fp{\mathfrak{p}} \def\fq{\mathfrak{q}} \def\fr{\mathfrak{r}} \def\fs{\mathfrak{s}} \def\ft{\mathfrak{t}} \def\fu{\mathfrak{u}} \def\fv{\mathfrak{v}} \def\fw{\mathfrak{w}} \def\fx{\mathfrak{x}} \def\fy{\mathfrak{y}} \def\fz{\mathfrak{z}}
\def\fgl{\mathfrak{gl}}  \def\fsl{\mathfrak{sl}}  \def\fso{\mathfrak{so}}  \def\fsp{\mathfrak{sp}}  
\def\GL{\mathrm{GL}} \def\SL{\mathrm{SL}}  \def\SP{\mathrm{SL}}

\def\<{\langle} \def\>{\rangle}
\usepackage{mathabx}
\def\acts{\lefttorightarrow}
\def\ad{\mathrm{ad}} 
\def\Aut{\mathrm{Aut}}
\def\Ann{\mathrm{Ann}}
\def\dim{\mathrm{dim}} 
\def\End{\mathrm{End}} 
\def\ev{\mathrm{ev}} 
\def\Fr{\mathcal{F}\mathrm{r}}
\def\half{\hbox{$\frac12$}}
\def\Hom{\mathrm{Hom}} 
\def\id{\mathrm{id}} 
\def\sgn{\mathrm{sgn}}  
\def\supp{\mathrm{supp}}  
\def\Tor{\mathrm{Tor}}
\def\tr{\mathrm{tr}} 
\def\vep{\varepsilon}
\def\f{\varphi}


\def\Obj{\mathrm{Obj}}
\def\normeq{\unlhd}
\def\Set{{\cS\mathrm{et}}}
\def\Fin{{\cF\mathrm{inSet}}}
\def\Set{{\cS\mathrm{et}}}
\def\Grp{{\cG\mathrm{rp}}}
\def\Ab{{\cA\mathrm{b}}}
\def\Mod{{\cM\mathrm{od}}}
\def\ab{\mathrm{ab}}
\def\lcm{\mathrm{lcm}}
\def\ZZn{\ZZ/n\ZZ}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{Expository Paper: Galois Groups of Polynomials}
\author{Chris Hayduk}
\date{December 15, 2020}
\maketitle

\begin{abstract}
Galois theory has been a fundamental topic in the overarching field of algebra. Its development spurred the creation of many concepts which are today central to the field, such a groups \cite{jorg, galoiswiki}. Most notably though, Galois theory furnished us with the ability to describe the solutions to polynomials of arbitrary degree, an achievement that eluded mathematicians for thousands of years \cite{jorg}. In this expository paper, we will build up the necessary background knowledge in polynomials and abstract algebra in order to understand Galois' elegant theorems. In the process, we will develop The Fundamental Theorem of Algebra, the division algorithm for polynomials, field extensions, and automorphisms. We will then make use of these concepts to introduce the Galois group and its applicability to polynomials. Through the use of Galois groups, we are able to abstract away many of the ``unnecessary'' details of these polynomials and focus on the characteristics we care about such as irreducibility, solvability, and the degree of the root operations, widening the range of polynomials which we are able to effectively work with \cite{jorg}.
\end{abstract}

\newpage
\section{Polynomials}

\subsection{Introduction}

A \textit{polynomial} is defined by Wikipedia as ``an expression consisting of variables and coefficients, that involves only the addition, subtraction, multiplication, and non-negative integer exponentiation of variables'' \cite{polynomialwiki}. To be more precise, we can define a \textit{polynomial} over the rational numbers, $QQ$, in the variable $x$ to be the expression,
\begin{align*}
p(x) = r_0 + r_1x + \cdots + r_nx^n
\end{align*} 

where $r_0, \ldots, r_n \in \QQ$, $0 \leq n \in \ZZ$, and $x$ is undefined \cite[\S 2.1, p. 36]{stewart}. We can denote the set of all polynomials over $\QQ$ in $x$ by $\QQ[x]$.

\par
Polynomials of this form have been a central theme of mathematics for thousands of years, dating back to at least the Babylonians of 1600 BC \cite[p. 2]{stewart}. During this early period of research into polynomials, mathematicians were primarily concerned with polynomials in one variable. That is, the polynomial was represented by an equation with a single variable that could potentially have separate different exponential terms. For example, the equation $x^2 + 2x + 1$ is a common polynomial in one variable. The variable $x$ is an element of a field. For earlier mathematicians, this usually meant rational numbers, until eventually real numbers were introduced. The term with the highest \textit{degree} (that is, the largest value of an exponent of $x$) gives us the degree of the polynomial. In our previous example, we have a polynomial in one variable with degree $2$. Formally, we can define this as follows,

\par
\textbf{Definition} (\cite[Definition 2.1]{stewart}). If $f$ is a polynomial and $f \neq 0$, then the \textit{degree} of $f$ is the highest power of $t$ occurring in $f$ with non-zero coefficient. We write $\partial f$ for the degree of $f$.

\par
Finding the zeros of polynomials was a very active field of research for many centuries, with the goal of finding a general, closed form solution for the polynomials of each degree \cite[p. 3-5]{stewart}. If we take a degree $1$ polynomial, such as $x + 1$, finding the zeros amounts to solving the equation $x + 1 = 0$, which is $x = -1$ by our basic rules of algebra and arithmetic. However, the situation rapidly becomes significantly more complicated as the degree of the polynomial increases.

\par
In the situation of \textit{quadratic polynomials} (that is, polynomials of degree $2$), we need to solve them using radicals. For example, the equation $x^2 - 2 = 0$ is solved by $x = \pm \sqrt{2}$. However, note here that, although our coefficients are in $\QQ$, our answer does not exist in $\QQ$. Thus, for quadratic equations, we must extend from $\QQ[x]$ to $\RR[x]$ in order to find a solution. Similarly, the equation $x^2 + 2 = 0$ is solved by $x = \pm \sqrt{-2}$. Hence, once we get to the case of degree $2$ polynomials, we need to go beyond real numbers and use the complex numbers ($\CC$) in order to furnish a general theory for their solution. We denote the set of such polynomials by $\CC[x]$. We can now give the general quadratic formula to solve equations of the form $ax^2 + bx + c = 0$, given by
\begin{align*}
x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
\end{align*}

Closed form equations of this kind were eventually found for cubic (degree $3$) and quartic (degree $4$) polynomials \cite[\S 1.4, p. 25-29]{stewart}. However, a closed form for solutions to quintic (degree $5$) polynomials continued to elude mathematics researchers for centuries \cite[\S 1.4, p. 31]{stewart}. Many mathematicians began to ask if the number system they were working in needed to be expanded yet again, just as the extensions to the real numbers and eventually the complex numbers allowed them to solve polynomials of greater complexity \cite[\S 2.2, p. 39]{stewart}. However, equipped with the following theorem, we can show that this is not the case \cite[\S 2.2, p. 41]{stewart}:

\begin{thm*}[{\cite[Thm.\ 2.4]{stewart}}, \textbf{The Fundamental Theorem of Algebra}] 
If $p(z)$ is a non-constant polynomial over $\CC$, then there exists $z_0 \in \CC$ such that $p(z_0) = 0$.
\end{thm*}

Hence, we can see that every polynomial over $\CC$ also has a root in $\CC$, avoiding the pitfall we ran into when considering $x^2 + 1 = 0$ over $\RR$. Thus, it is not necessary to expand to a more ``general'' number system in order to solve higher degree polynomials.

\subsection{Factorization}

We can now begin to discuss the factorization of polynomials. Factoring a polynomial into several polynomials of smaller degree allows us to simply the root-finding problem, as we can then search for the roots of the new polynomials, rather than the original equation. A familiar example would be $x^2 - 1$. This polynomial can be factored into $(x+1)(x-1)$, and so finding the roots of $x^2 - 1 = 0$ simplifies to finding the roots of $x+1 = 0$ and $x - 1 = 0$. The two degree $1$ equations yield $x = -1$ and $x = 1$ quite quickly.

\par
To formalize factorization of polynomials, we first need to introduce a few theorems:

\begin{thm*}[{\cite[Thm.\ 2.5]{stewart}}, \textbf{Remainder Theorem}] 
Let $p(x) \in \CC[x]$ with $\partial p \geq 1$, and let $\alpha \in \CC$.
\begin{enumerate}
\item There exist $q(t) \in \CC[x]$ and $r \in \CC$ such that $p(x) = (x - \alpha)q(x) + r$
\item The constant $r$ satisfies $r = p(\alpha)$
\end{enumerate}
\end{thm*}

\begin{prop*}[{\cite[Prop.\ 3.1]{stewart}}, \textbf{Division Algorithm}] 
Let $f$ and $g$ be polynomials over $K$ and suppose that $f$ is non-zero. Then there exist unique polynomials $q$ and $r$ over $K$, such that $g = fq + r$ and has strictly smaller degree than $f$.
\end{prop*}

The above theorem and proposition allow us to divide polynomials by other polynomials, paving the way for us to discuss the polynomial equivalent of prime numbers: \textit{irreducible polynomials}. A non-constant polynomial over a subring $R$ of $\CC$ is \textit{reducible} if it is a product of two polynomials over $R$ of smaller degree. Otherwise it is \textit{irreducible} \cite[\S 3.2, p. 51]{stewart}.

\textbf{Examples.}
\begin{enumerate}
\item All degree $1$ polynomials are irreducible
\item As above, $x^2 - 1 = (x + 1)(x - 1)$ and is hence a reducible polynomial
\end{enumerate}

Now we can assert an analogue of prime factorization for polynomials in $\CC$:

\begin{thm*}[{\cite[Thm.\ 3.12]{stewart}}] 
Any non-zero polynomial over a subring $R$ of $\CC$ is a product of irreducible polynomials over $R$.
\end{thm*}

\begin{proof}
Let $g$ be a polynomial over $R$ such that $g \neq 0$. We will proceed with this proof through induction. Let us start with cases $\partial g = 0$ and $\partial g = 1$. A fact about polynomials is, for two polynomial $f, h$ over $R$, we have $\partial fh = \partial f + \partial h$. So in both cases for $g$, it is not possible to find two polynomials $f, h$ with degree smaller than $g$ such that $g = fh$. Now fix $n \in \NN$ with $n > 1$, let $\partial g = n$, and suppose for all $k < n$, we have that polynomials of $\partial k$ are reducible. We have two possible cases: either $g$ is irreducible (in which case we are done) or $g = fh$ for two polynomial $f, h$ with $\partial f, \partial h < \partial g$. But by our induction hypothesis, $f$ and $g$ are products of irreducible polynomials, and so $g$ is the product of irreducible polynomials.
\end{proof}

The framework for the above poor is taken from: \cite[\S 3.2, p. 52]{stewart}.

\subsection{Zeros of Polynomials}

We can now discuss some useful properties of the zeros of polynomials. If $R$ is a subring of $\CC$ and $f$ is a polynomial over $R$, then an element $\alpha \in R$ such that $f(\alpha) = 0$ is a \textit{zero of f in R}.

\textbf{Definition} (\cite[Definition 3.26]{stewart}). Let $f$ be a polynomial over the subfield $K$ of $\CC$. An element $\alpha \in K$ is a \textit{simple zero} of $f$ if $(x - \alpha) | f(x)$ but $(x - \alpha)^2$ does not divide $f(x)$. The element $\alpha$ is a zero of $f$ of \textit{multiplicity} $m$ if $(x - \alpha)^m | f(x)$ but $(x - \alpha)^{m+1}$ does not divide $f(x)$. Zeros of multiplicity greater than 1 are \textit{repeated} or \textit{multiple zeros}.

\begin{lemma*}[{\cite[Lemma\ 3.27]{stewart}}] 
Let $f$ be a non-zero polynomial over the subfield $K$ of $\CC$, and lets its distinct zeros be $\alpha_1, \ldots, \alpha_r$ with multiplicities $m_1, \ldots, m_r$ respectively. Then,
\begin{align*}
f(x) = (x - \alpha_1)^{m_1} \cdots (x - \alpha_r)^{m_r}g(x)
\end{align*}
where $g$ gas no zeros in K. Conversely, if the above equation holds and $g$ has no zeros in $K$, then the zeros of $f$ in $K$ are $\alpha_1, \ldots, \alpha_r$ with multiplicities $m_1, \ldots, m_r$ respectively.
\end{lemma*}

Lastly, from this lemma we get an important theorem:

\begin{thm*}[{\cite[Thm.\ 3.28]{stewart}}] 
The number of zeros of a nonzero polynomial over a subfield of $\CC$, counted according to multiplicity, is less than or equal to its degree.
\end{thm*}

\section{Field Theory}

\subsection{Introduction}

While Galois Theory initially was treated by examining polynomials directly, algebraists eventually switched to examining the more general field extensions related to a polynomial \cite[\S 4, p. 63]{stewart}. We'll start by providing some definitions regarding fields in order to have the necessary background to discuss field extensions.

\textbf{Definition} (\cite[\S 7.1]{dummit}). A ring $R$ with identity $1$, where $1 \neq 0$, is called a \textit{division ring} (or \textit{skew field}) if every nonzero element $a \in R$ has a multiplicative inverse, i.e., there exists $b \in R$ such that $ab = ba = 1$. A commutative division ring is called a \textit{field}.

\textbf{Definition} (\cite[\S 7.1]{dummit}). A \textit{subring} of the ring $R$ is a subgroup of $R$ that is closed under multiplication.

\textbf{Definition} {\cite[\S 1.2]{stewart}] A \textit{monomorphism} is a homomorphism which is injective but not necessarily surjective.

Now, with these three definitions in mind, we can introduce field extensions.

\subsection{Field Extensions}

We define a field extensions as follows:

\textbf{Definition} (\cite[Definition 4.1]{stewart}). A \textit{field extension} is a monomorphism $\tau: K \to L$ where $K$ and $L$ are subfields of $\CC$. We say that $K$ is the \textit{small} field and $L$ is the \textit{large} field.

We make this distinction between $K$ and $L$ as the small and large fields due to the properties of $\tau$ as a monomorphism. Since $\tau$ is injective but not necessarily surjective, we know that $L$ is at least as large as $K$ but could potentially be larger. Hence, we call it the \textit{large} field. We can also use the notation $L:K$ to denote a field extension, and we say that $L$ is an \textit{extension} of $K$. We now need to introduce two more definitions before moving on to simple extensions:

\textbf{Definition} (\cite[Definition 4.3]{stewart}). Let $X$ be a subset of $\CC$. Then the subfield of $\CC$ \textit{generated} by $X$ is the intersection of all subfields of $\CC$ that contain $X$

\textbf{Definition} (\cite[Definition 4.7]{stewart}). If $L:K$ is a field extension and $Y$ is a subset of $L$, then the subfield of $\CC$ generated by $K \cup Y$ is written $K(Y)$ and is said to be obtained from $K$ by \textit{adjoining} $Y$.

\newpage
\subsection{Simple Extensions}

Simple extensions are field extensions obtained by adjoining one element:

\textbf{Definition} (\cite[Definition 4.10]{stewart}). A \textit{simple extension} is a field extension $L:K$ such that $L = K(\alpha)$ for some $\alpha \in L$.

\textbf{Example.} We have that $\QQ(\sqrt{2}) = \{p + q\sqrt{2} \ | \ p, q \in \QQ\}$ is a simple extension of the field $\QQ$.

Simple extensions can be classified into two distinct types: algebraic and transcendental. If $K$ is a subfield $\CC$ and $\alpha \in \CC$, we say $\alpha$ is \textit{algebraic} over $K$ if there exists a non-zero polynomial $p$ over $K$ such that $p(\alpha) = 0$. If not, we say that $\alpha$ is \textit{transcendental} over $K$ \cite[\S 5.1, p. 71]{stewart}.

\par
Now we will look at constructing simple algebraic extensions. This amounts to finding a specific type of polynomial $f$ such that $f(\alpha) = 0$ known as a minimal polynomial \cite[\S 5.2]{stewart}. However, we must define another polynomial concept before introducing the definition of a minimal polynomial. A \textit{monic polynomial} is a polynomial $f(x) = a_0 + a_1x + \cdots + a_nx^n$ such that $a_n = 1$ \cite[\S 5.2]{stewart}. That is, the term in the polynomial with the largest degree has a corresponding coefficient of $1$. Now, equipped with this definition, we can define a minimal polynomial:

\textbf{Definition} (\cite[Definition 5.5]{stewart}). Let $L : K$ be a field extension, and suppose that $\alpha \in L$ is algebraic over $K$. Then the \textit{minimal polynomial} of $\alpha$ over $K$ is the unique monic polynomial $m$ over $K$ of smallest degree such that $m(\alpha) = 0$.



\section{Galois Theory}

\subsection{Overview}

We can now return to the main objective of our work: finding a general solution for polynomials of degree $5$ (or higher). The general idea Galois used to approach this idea was associating to each polynomial $p \in \CC[x]$ a group of permutations which we now call the \textit{Galois group} of $p$ \cite[\S 8, p. 107]{stewart}. In this way, we are able to reduce very difficult questions about a polynomial to simpler questions about its Galois group. Galois specifically introduced this concept in order to study solutions to quintic polynomials and, as we will soon demonstrate, he showed that there is no quintic formula \cite{galoiswiki}. Moreover, he was able to describe \textit{which} degree $5$ polynomials are solvable by radicals \cite{galoiswiki}.

We will start by illustrating an example from \cite[\S 8.2]{stewart} in order to give some intuition behind Galois theory. Consider the polynomial $f(x) = x^4 - 4x^2 - 5 = 0$. As discussed before, we can factor this polynomial into the product of irreducible polynomials, yielding $f(x) = (x^2+1)(x^2-5) = 0$. As a result, we find the following roots: $x = i, -i, \sqrt{5}, -\sqrt{5}$. There is a natural sort of relation between $i, -i$ and $\sqrt{5}, -\sqrt{5}$, and we actually see that the elements in each of these pairs are indistinguishable from the other element in the pair algebraically. That is, if we construct a polynomial equation with rational coefficients that is satisfied by a subset of our four roots, we can interchange $i$ and $-i$ or $\sqrt{5}$ and $-\sqrt{5}$ without altering the equation. If we label the roots in the following manner,
\begin{align*}
\alpha = i, \ \beta = -i, \ \gamma = \sqrt{5}, \ \delta = -\sqrt{5}
\end{align*}

then we can label the ``allowable'' symmetries using the notation from Dummit and Foote:
\begin{align*}
(\alpha \beta), \ (\alpha \beta)(\gamma \delta), \ (\gamma \delta), \ I
\end{align*}

where $I$ is the identity. These four symmetries make up the symmetry group of the roots of our polynomial $f(x)$. We can use these polynomial equations of our roots to solve any polynomial that shares this same root structure. That is, the solutions of a polynomial are tied directly to the structure of the symmetric group of its roots.

\subsection{Polynomials and Extensions}

First, we need to define a new kind of automorphism:

\textbf{Definition} (\cite[Definition 8.1]{stewart}). Let $L : K$ be a field extension, so that $K$ is a subfield of the subfield $L$ of $\CC$. A $K$-\textit{automorphism} of $L$ is an automorphism $\alpha$ of $L$ such that
\begin{align*}
\alpha(k) = k \text{    for all } k \in K
\end{align*}

We say that $\alpha$ \textit{fixes} $k \in K$ if the above holds.

\par
Now with the above definition, we can state the following theorem:

\begin{thm*}[{\cite[Thm.\ 8.2]{stewart}}] 
If $L : K$ is a field extension, then the set of all $K$-automorphisms of $L$ forms a group under composition of maps.
\end{thm*}

\begin{proof}
We need to show that the set of all $K$-automorphisms of $L$ has an identity element and is closed under composition and inverses. Note that an automorphism is an isomorphism of a set with itself. Thus, note that the identity map is by definition an automorphism since the inverse of every element is itself. Moreover, since $I(k) = k$ for every $k \in K$, we have that $I$ fixes $K$ in $L$. Thus the identity map is in the set of all $K$-automorphhisms of $L$.

\par
Now let $\alpha, \beta$ be in the set of all $K$-automorphisms of $L$. We have that $\alpha \beta$ must also be an automorphism. In addition, for every $k \in K$, we have that
\begin{align*}
\alpha(\beta(k)) &= \alpha(k)\\
&= k
\end{align*}

Hence, $\alpha \beta$ is in the set of all $K$-automorphisms of $L$.

\par
Lastly, let $\alpha$ be in the set of all $K$-automorphisms of $L$. We need to show that $\alpha^{-1}$ is in the set as well. Since $\alpha$ is bijective, so is $\alpha^{-1}$. In addition, since $\alpha(xy) = \alpha(x)\alpha(y)$ for every $x, y \in L$, we have that,
\begin{align*}
\alpha^{-1}(\alpha(x)\alpha(y)) &= \alpha^{-1}(\alpha(xy))\\
&= xy
\end{align*}

and
\begin{align*}
\alpha^{-1}(\alpha(x))\alpha^{-1}(\alpha(y)) = xy
\end{align*}

Thus, $\alpha^{-1}$ is an automorphism of $L$. Now note that since $\alpha(k) = k$ for every $k \in K$, we have that,
\begin{align*}
&\alpha^{-1}(\alpha(k)) = \alpha^{-1}(k)\\
\implies &k = \alpha^{-1}(k)
\end{align*}

Hence, $\alpha^{-1}$ fixes $K$ in $L$ and is thus a $K$-automorphism of $L$. As a result, we have that the set of all $K$-automorphisms of $L$ forms a group.
\end{proof}

The framework of the above proof is given in \cite[\S 8.5, p. 113]{stewart}.

\par
We can now introduce our most important definition so far:

\textbf{Definition} (\cite[Definition 8.3]{stewart}). The \textit{Galois group} $\Gamma(L:K)$ of a field extension $L:K$ is the group of all $K$-automorphisms of $L$ under the operation of composition of maps.

\par
\textbf{Example} \cite[Example 8.4]{stewart}. Let $c$ be the real cube root of $2$ and consider $\QQ(c) : \QQ$. If $\alpha$ is a $\QQ$-automorphism of $\QQ(c)$, then
\begin{align*}
(\alpha(c))^3 = \alpha(c)^3 = \alpha(2) = 2
\end{align*}

Since $\QQ(c) \subset \RR$, we must have $\alpha(c) = c$. Hence $\alpha$ is the identity map and $\Gamma(\QQ(c):\QQ)$ has order $1$.

\newpage
\subsection{Galois Group of an Equation}

The core feature of Galois groups in relation to polynomials is that all the main properties of a polynomial, such as irreducibility, solvability, and the degree of the root operations, can be determined from the equation's Galois group rather than by making any explicit reference to the polynomial itself \cite[\S 9.1]{jorg}. In addition, the number of possible Galois groups is significantly smaller than the number of possible equations. Hence, describing the properties of the Galois groups for polynomials of a given degree is significantly easier than looking at the properties of the polynomials themselves \cite[\S 9.1]{jorg}.

\par
We are going to introduce an alternative definition here for the Galois group which will facilitate computations with polynomials:

\textbf{Definition} (\cite[Definition 9.2]{jorg}). For a polynomial equation with multiple solutions (i.e. all of its solutions are distinct) whose coefficients lie in a field $K$, the \textit{Galois group} (over the field $K$) is the set of all permutations $\sigma$ in the symmetric group $S_n$ that permute the indices $1, \ldots, n$ of the solutions $x_1, \ldots, x)n$ in such a way that for every polynomial $h(X_1, \ldots, X_n)$ with coefficients in $K$ and $h(x_1, \ldots, x_n) = 0$, we have $h(x_{\sigma(1)}, \ldots, x_{\sigma(n)}) = 0$.

\par
Note that the permutations included in the Galois group of an equation can be assembled into a group table, which describes the multiplicative relationship between the permutations. With that structure in mind for the Galois group, we can attempt to define the solvability of an irreducible equation:

\begin{thm*}[{\cite[Thm.\ 9.3]{jorg}}] 
An irreducible equation is solvable in radicals precisely when the Galois group can be reduced step by step to a one-element Galois group, containing only the identity permutation, where each step corresponds to a decomposition of the (suitably ordered) group table into $m^2$ squares each of which contains the $m$th part of the permutations.\end{thm*}

\par
\textbf{Example.} Let us consider the polynomial $f(x) = x^2 - 1$ over $\QQ$. The roots of this polynomial are $x_1 = \sqrt{2}$ and $x_2 = -\sqrt{2}$. Since there are $2$ distinct solutions, we have two possible permutations for the roots,
\begin{align*}
x_{\sigma_0(1)} &= x_1\\
x_{\sigma_0(2)} &= x_2
\end{align*}

and,
\begin{align*}
x_{\sigma_1(1)} &= x_2\\
x_{\sigma_1(2)} &= x_1
\end{align*}

Thus, we end up with the following group table,
\begin{align*}
\kbordermatrix{
    & \sigma_0 & \sigma_1\\
    \sigma_0 & \sigma_0 & \sigma_1\\
    \sigma_1 & \sigma_1 & \sigma_0
  }
\end{align*}

Now let us adjoin $\sqrt{2}$ to $\QQ$. That is, we are now considering the field extension $\QQ(\sqrt{2}) = \{a + b\sqrt{2} \ | \ a,b \in \QQ\}$. In this field extension, our roots $x_1$ and $x_2$  in terms of rational numbers and the adjoined $\sqrt{2}$ using the four basic arithmetic operations. So we need to consider $X_1 - x_1$ and $X_2 - x_2$. And hence, the Galois group only contains the identity permutation, $\sigma_0$. Thus, we have reduced the group table to the Galois group with a single element as required.

\par
Now we are brought to a key result by Galois regarding the solvability in radicals of equations of prime degree,
\begin{thm*}[{\cite[Thm.\ 9.4]{jorg}}] 
An irreducible equation of prime degree is solvable in radicals if and only if all the solutions can be expressed as polynomials in two arbitrary solutions.
\end{thm*}

Now consider the polynomial $x^5 - 17x - 17 = 0$. The polynomial has three real and two complex roots and is irreducible. It is impossible to use any two of the real roots to express the other solutions in terms of polynomials, so the equation is unsolvable by the above theorem.

\newpage
\section{Conclusion}

Galois' main point of relating the symmetric group of polynomials' roots to its solutions provided an elegant and powerful new paradigm for addressing the solutions of polynomials. Each polynomial no longer needed to be evaluated individually. Instead, we can examine the Galois group of a polynomial in order to determine its properties and relate it to other polynomials. In particular, this approach significantly reduced the complexity of the determining the solvability in radicals of the quintic equation which, as we discussed in the introduction, was a primary focus of mathematicians for centuries.

\par
Moving beyond roots of polynomials, Galois theory's powerful applicability to problems in classical algebra demonstrated the strength continually abstracting the objects that we are working with. Its development laid much of the groundwork for concepts which we've covered in class such as groups and fields. As a result, Galois theory marked one of the most important advancements and developments in the field of algebra.

\newpage
\begin{thebibliography}{9}

\bibitem{jorg}
Bewersdorff, Jorg. \textit{Galois Theory for Beginners}. American Mathematical Society, 2006. 

\bibitem{juliusz}
Brzeziński, Juliusz. \textit{Galois Theory Through Exercises}. Springer, 2018. 

\bibitem{dummit}
Dummit, David Steven., and Richard M. Foote. \textit{Abstract Algebra}. 3rd ed., John Wiley \& Sons, 2004.

\bibitem{stewart}
Stewart, Ian. \textit{Galois Theory}. Chapman \& Hall/CRC, 2015.  

\bibitem{galoiswiki} 
``Wikipedia -- Galois Theory.” \textit{Wikipedia}, Wikimedia Foundation,\\ \texttt{https://en.wikipedia.org/wiki/Galois\_theory}. 

\bibitem{fundamentaltheoremwiki}
``Wikipedia -- Fundamental Theorem of Galois Theory.” \textit{Wikipedia}, Wikimedia Foundation,\\ \texttt{https://en.wikipedia.org/wiki/Fundamental\_theorem\_of\_Galois\_theory}. 

\bibitem{polynomialwiki}
``Wikipedia -- Polynomial.” \textit{Wikipedia}, Wikimedia Foundation,\\ \texttt{https://en.wikipedia.org/wiki/Polynomial}. 
\end{thebibliography}

\end{document}